\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\title{Can an Unknowing Participant distinguish between Procedurally generated and Human designed Interiors? - WIP title}

\author{Thomas O'Leary}

\maketitle

\begin{abstract}
    What's the problem? What am I looking at? How does that help solve the problem? \\
    \\
    Opening, Challenge, Action, Resolution \\
    \\
    Decorating an interior can be time consuming. \emph{Define time consuming?}.
    \\
    Attempt to see if procedural generated interiors can be percieved as human designed.
    Comparing the two together and see if participants prefer the procedurally generated designs.
\end{abstract}

\section{Introduction}
    What is Procedural generation? 
    What specifically is Procedural interior generation?
    Explain more why this could be a valuable tool for games?\\
    \\
    Why should it be compared to human created interiors?
    
\section{Background \& Supporting Literature}
    Go into a level of detail about how procedural interior generation can be done. (Different methods etc)
    \\
    Paper that I read. Only writing this to test that my .bib file is working. \cite{real-time}

\section{Research Question}
    From the above sources, I have formed \textbf{actual research question that's totally not wip anymore}
    \subsection{hypothesis \& null hypothesis}

\section{Artifact}
    \subsection{What will be made}
        AI that procedurally generates interior at runtime in a pre-defined room size and access to pre-made furniture assets. \\
        Will be later compared with human designed interiors (being given the same room size and assets)


    \subsection{How will I ensure Quality}
        Quality control. Roadmap? Unit Testing? Integration testing?

    \subsection{How will I create it}
        The AI will be made in the Unity game engine (Version 2020.3.12f1)

    \subsection{Why will this answer the questions}

\section{Research Methodology}
    \subsection{Experimental Design}

    \subsection{Limitations}
        Time, resources

    \subsection{Sampling Plan}
        Sample size, sampling method

    \subsection{Data management plan}
        Managing, collecting, \& storing data

    \subsection{Data Analysis}

    \subsection{Ethical Considerations}

\section{Appendix}
    Data analysis code, supporting screenshots, list of unit tests \& testing plan

\bibliographystyle{ieeetr}
\bibliography{bibliography}

\end{document}