\section{Conclusion \& Future Work}

As discussed in \hyperref[issues]{Section VII}, particular elements of the research study can be adjusted to possibly administrate more beneficial data in whether participants can distinguish between Multi-Agent designed and Human designed Interiors.
\\
\\
Inspired by how \italic{P. Henderson, et al.} \cite{constrained-layouts} and \italic{L.-F. Yu et al.} \cite{make-it-home} handle it in their work - implementing different viewing frustums for the layouts in the experimental design, could potentially open an alley for more thoughtful decisions made by participants as they have more information to take in regarding each room layout in both stages of the study. It could allow them to analyse the room in more depth and perhaps visualise the room with much more ease with the multiple perspectives.
\\
\\
Another aspect of the study that could be adjusted is the selection of participants. By expanding the participation selection pool, a much varied range of data could have been collected due to the varied knowledge of participants - potentially having participants with varied knowledge in digital games, varied knowledge of what AI is and potentially varied knowledge in interior design which could have a much bigger impact in the first stage of the study.
\\
\\
To conclude, this research paper sought out to see if an unknowing participant was able to distinguish between Human and Artificial Intelligence designed (through the use of a Multi-Agent system) interiors. 5 pairs of both types of interiors were held to the challenge in a 2 staged A/B test that gained the data from 56 willing participants.
In the first stage, participants were informed to select which room they preferred in each pair and in the second, participants were informed of the involvement of the Artefact and to proceed in picking which interior layout was made by this Artefact.
Although both hypotheses failed to reject their respective nulls, the data collected from this research study can be used as preliminary results going forward to help any future studies surrounding Procedural Interior Generation and its comparison to that of Human design.