\section{Introduction}

Urban open world games such as the Grand Theft Auto series[cite], The Division series[cite] and the Batman Arkham series[cite]
have such large built-up areas for players to venture in, but many buildings are blocked off - 
if you're lucky to have access to a building you are still very limited to the rooms you are able to enter.
Possibly ruining the immersion of the game for players.

This problem could be fixed by having developers designing each and every room in every single building within the vast urban environment.
But this would become a very time-consuming and impractical task.

Using Procedural Generation (PCG), this largely time-consuming task of designing room interiors can be automated. And can possibly help maintain a player's immersion within the game.

An issue with this however is that a PCG tool could potentially be easily identifiable. This 

Through my literature review though I have found many implementations and techniques of Procedural Interior Generation (PCIG), none of these get compared to Human designed interiors. 

This study looks to see if a participant is able to tell the difference between Human designed and AI generated interiors.

%urban open world games such as the Grand Theft Auto series, Watchdogs series and the Batman Arkham series
%have such large built-up urban areas for players to venture in but many buildings/rooms inside buildings are blocked off, stopping players from exploring inside.

%Assassins Creed Unity

%simply, designers could model these interiors by themselves but due to the ever increasing nature of open world games - this would become and already is impractical and very time consuming/

%using procedural generation techniques, this time consuming task can be automated to allow designers to focus on other things blah blah blah

%the issue at hand is procedural generation can tend to be repetitive, dull and could potentially ruin the emersion of a game.

%this study looks to see if someone is able to tell the difference between hand made and AI generated interiors.
